Empirical normative theories

### 2020-07-24 simple.tex
New proof and defs started using coalition attacks

	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.
\end{remark}

>>>>

	Thus, maybe need to define $\args' \ibeats[\prime] \ar_0$ iff $\exists \hist… \ileadstost \phi$.

	Given $i \in I, \phi \in \Phi$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$. 
	Define $\args \ibeatscoalstr \ar_0$ iff $\forall \hist \in \allhist: [\hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0] ⇒ \hist \nileadstost \phi$, that is, iff no $\hist$ that end with $\args$ followed by $\ar_0$ lead to $\phi$.
	Define $\ar_1 \ibeats \ar_0$ iff $\exists \set{\ar_1} \subseteq \args \subseteq \allargs \suchthat \args \ibeatscoal \ar_0 \land \args \setminus \set{\ar_1} \nibeatscoalstr \ar_0$.

	Lemma. Given any $\ar_0$ that $i$-defends $\phi$, $\forall \args \subseteq \allargs: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$. Observe that the implication holds for $\args = \emptyset$, because $\emptyset \nibeatscoal \ar_0$ as $\ar_0$ $i$-defends $\phi$. Now, given $k \in \N$, assume that $\forall \args \subseteq \allargs \suchthat \card{\args} = k: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$, and let us show that $\forall \args \subseteq \allargs \suchthat \card{\args} = k + 1: [\args \ibeatscoal \ar_0 ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0]$.
	Consider $\args \subseteq \allargs \suchthat \card{\args} = k + 1 \land \args \ibeatscoal \ar_0$. One of the following two cases hold. First case: $\forall \args' \subset \args \suchthat \card{\args'} = k: \args \nibeatscoalstr \ar_0$. Then, $\forall \ar_1 \in \args: \ar_1 \ibeats \ar_0$. Second case: $\exists \args' \subset \args \suchthat \card{\args'} = k \land \args' \ibeatscoalstr \ar_0$. Then, $\args' \ibeatscoal \ar_0$ (noting that ${\ibeatscoalstr} \subseteq {\ibeatscoal}$), thus $\exists \ar_1 \in \args' \suchthat \ar_1 \ibeats \ar_0$ (using the hypothesis of recurrence), hence, $\exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$.

	This lemma permits to deduce that, given $\ar_0$ that $i$-defends $\phi$, $\hist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$, and $\args = \gbeatsinv(\ar_0) \cap \hist$: $\args ≠ \emptyset ⇒ \exists \ar_1 \in \args \suchthat \ar_1 \ibeats \ar_0$. This holds because in that case, $\args \ibeatscoal \ar_0$.

	Problem happens in the following case. $\ar'_1$ alone is uncertain, meaning $\exists \hist = (… \ar'_1 … \ar_0) \nileadstost \phi$ and $\exists \hist = (…, \ar'_1, \ar_0) \ileadstost \phi$. Then, a counter-theory $\delta$ may claim that $\ar'_1$ alone is ineffective: suffice to show the example $(…, \ar'_1, \ar_0) \ileadstost \phi$. Whereas in fact $\ar'_1$ alone is sometimes effective. Then, $\args = \set{\ar_1, \ar'_1}$ may be claimed to be effective by combination effect (and $\ar'_1$ can’t be blamed, although it should, as $\delta$ has “proven” it ineffective). Thus, $\ar_2$, defending against $\ar_1$, ends up in $\gargs$. Assume $\ar_1$ is innocuous for $i$ (otherwise, no problem, as $\ar_2$ is legitimate) ($\ar_1$ could be efficient for others than $i$, which justifies $\ar_1 \gbeats \ar_0$). Then $\ar_2$ shouldn’t be played, it is only included as a result of the weak demand about proving that $\ar'_1$ is ineffective.

Note that if we agree that $\ar'_1$ is uncertain, then $\gamma$ should play $\ar'_2$ to answer the coalition $\args$ attack (as required even without the coalitions definition), not $\ar_2$. But this conflicts with the formal definitions. Note that if $\ar'_1$ is known as uncertain for everybody, there is no problem, as $\gamma$ should include $\ar'_2$ from the start. Problem happens if $\ar'_1$ is suspected uncertain for some and inefficient for others.

	Here is a similar problem: assume $\ar_1$ and $\ar'_1$ are uncertain for some and innocuous for others (not necessarily the same). Assume we observed $(…, \ar_1, \ar_0) \ileadstost \phi$ (without $\ar'_1$) and $(…, \ar'_1, \ar_0) \ileadstost \phi$ (without $\ar_1$, and imagining this would be possible to know); but $\set{\ar_1, \ar'_1}$ attacks $\ar_0$. Then we ignore whether, for $i$, $\ar_1$ or $\ar'_1$ is innocuous; and thus ignore whether $\ar_2$ or $\ar'_2$ should be played. The right answer is probably: play $\ar_2 + \ar'_2$. In fact, suffices to assume that, whenever such situation can happen, $\gamma$ has planned that $\ar_2$ be attacked by $\ar'_1$, and conversely, and then we get immediately that $\ar_2 + \ar'_2$ is involved. (But also that $\ar_2$ should be defended, whereas this is perhaps too demanding?)
\end{remark}
